Composable Generalized Consensus

### 2016-01-07 paper/abstract4.tex
Work on the abstract: shortening.

To lower the cost of designing new SMR algorithms, we present a framework for composing independent and reusable SMR modules. 
An SMR module is an SMR algorithm augmented with a composition interface. 
In the composition of two modules, the first module starts executing and can abort its execution and pass the baton to the second module at any time.
Our composition theorem guarantees that the result of composing two SMR modules is again an SMR module and a correct SMR algorithm.
Module composition can be dynamic; therefore, our framework allows building SMR algorithms that choose and switch at runtime between a set of modules, and that can be augmented with new modules at any time.

To help design new modules in practice, we propose several TLA$^+$ specifications that each
provide a template to devise new modules with the help of the TLA$^+$ tools.
Using our specifications, we demonstrate that several well-known SMR algorithms can be made modular and composed to form a versatile SMR algorithm.

>>>>

To lower the cost of designing new SMR algorithms, we present a framework for composing SMR modules whose analysis can be done in isolation and reused. 
An SMR module is an SMR algorithm augmented with a composition interface and satisfying a specification called Composable Generalized Consensus. 
In the composition of two modules, the first module starts executing and can abort its execution and pass the baton to the second module at any time.
Our composition theorem guarantees that the composition of two SMR modules is itself an SMR module. %; therefore, composition can be applied repeatedly to a sequence of modules.
Module composition can be dynamic; therefore, our framework allows building SMR algorithms that choose and switch at runtime between a set of modules, and that can be augmented with new modules at any time.

To help design new modules in practice, we propose TLA$^+$ specifications that each
provide a template to devise new modules with the help of the TLA$^+$ tools.
Using our specifications, we demonstrate that several well-known SMR algorithms can be made modular and composed to form a versatile SMR algorithm.
